Hyperspectral tree defoliation modeling with a focus on feature-selection and model interpretation

### 2019-06-23 code/98-paper/journal/manuscript.tex
change title
add list of simple filters

%% arara: indent: {overwrite: yes}

@@

	\title{Modeling defoliation as a proxy for tree health: A case study using machine-learning and hyperspectral remote sensing data}

	%% Group authors per affiliation:
	\author[FSU]{Patrick Schratz}
	\cortext[mycorrespondingauthor]{Corresponding author}
	\ead{patrick.schratz@uni-jena.de}

@@

% Ensemble filter methods
Besides the concept of choosing a specific filter method to rank variables, studies showed that combining several filters using statistical operations such as "minimum", "mean" or "sum" are able to enhance the predictive performance of the resulting models \citep{abeel2010, drotar2017a}.
This aligns with the recent rise of the "ensemble" approach in machine-learning which uses stacking to combine the predictions of multiple models \citep{polikar2012, feurer2015}.
In this work the "Borda" ensemble filter was applied \citep{drotar2017a}.
Here, the ranking is based on the sum of all single filters.

Most filter methods are correlation or entropy based.
A list of all filter methods used in this work along with their respective formulas can be found in Appendix X.
% TODO: Link appendix
% TODO: List filter methods

% I grouped these two since we focus on filter methods in this study - or is this already a bit biased towards filter methods?
\subsubsection{Other approaches}

>>>>

% arara: indent: {overwrite: yes}

@@

	\title{Hyperspectral tree defoliation modeling with a focus on feature-selection and model interpretation}
	%% Group authors per affiliation:
	\author[FSU]{Patrick Schratz}
	\cortext[mycorrespondingauthor]{Corresponding author}
	\ead{patrick.schratz@uni-jena.de}

@@

\paragraph{Ensemble filter methods}

% Ensemble filter methods
Besides the concept of choosing a specific filter method to rank variables, studies showed that combining several filters using statistical operations such as "minimum", "mean" or "sum" are able to enhance the predictive performance of the resulting models \citep{abeel2010, drotar2017a}.
This approach is referred to as "ensemble filter" \citep{dietterich2000}.
Ensemble filters align with the recent rise of the "ensemble" approach in machine-learning which uses stacking to combine the predictions of multiple models, aiming to enhence predictive performance \citep{polikar2012, feurer2015}.
In this work the "Borda" ensemble filter was applied \citep{drotar2017a}.
The final order is the sum of all single filters ranking.

\paragraph{Ensuring a fair weighting in the ensemble}
Filter methods can be grouped into classes: Correlation based, entropy based, linear and non-linear methods.
It is important to not give certain classes too much weight in the ensemble as otherwise the final result will be biased.
This was taken care of by comparing the linear correlations of all generated filter values for each method against each other.
In case filters showed high correlations with each other, these were not included into the ensemble filter.
The goal was to create an ensemble filter showing low to medium correlations with each other.

\paragraph{Description of used filter methods}

Filter methods can be classified as follows:

\begin{itemize}
	\item univariate/multivariate (scoring based on a single variable / multiple variables)
	\item linear/non-linear (calculation of linear/non-linear interaction terms)
	\item entropy/correlation (scoring based on derivations of entropy or correlation based approaches)
\end{itemize}

% filter methods
\begin{table}[b!]
\centering
\caption[t]{List of filter methods used in this work}
\begingroup\footnotesize
\begin{tabular}{lll}
	\\
	Name                                         & Group                             & Reference          \\
	\hline
	Linear correlation (Pearson)                 & univariate, linear, correlation   & \cite{pearson1901} \\
	Information gain                             & univariate, non-linear, entropy   & \cite{quinlan1986} \\
	Minimum redundancy, maximum relevance        & multivariate, non-linear, entropy & \cite{zhao2013}    \\
	Carscore                                     & multivariate, linear, correlation & \cite{zuber2011}   \\
	Relief                                       & multivariate, linear, entropy,    & \cite{kira1992}    \\
	Conditional minimal information maximization & multivariate, linear, entropy     & \cite{fleuret2004}
\end{tabular}
\endgroup
\label{tab:filter-methods}
\end{table}

% I grouped these two since we focus on filter methods in this study - or is this already a bit biased towards filter methods?
\subsubsection{Wrapper methods and PCA}
